%-------------------------
% Resume in Latex
% Author : Amitabh Sharma
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
% \usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\usepackage{xcolor}
\usepackage[colorlinks = true,
            linkcolor = blue,
            urlcolor  = blue,
            citecolor = blue,
            anchorcolor = blue]{hyperref}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small #3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small #1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
%----------HEADING----------
\begin{center}
    {\Huge \scshape Amitabh Sharma} \\ \vspace{1pt}
    International Institute of Information Technology, Hyderabad \\ \vspace{1pt}
    \footnotesize {\raisebox{-0.2\height}\faEnvelope\ \underline{amitabh.sharma@research.iiit.ac.in}}
    \vspace{+2pt}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {International Institute of Information Technology, Hyderabad}{Aug 2022 -- Present}
      {MS by Research (Robotics) \quad CGPA: 9.67/10.00}{\textbf{Supervisor:} Dr. Spandan Roy}
    \resumeSubheading
      {Birla Institue of Technology and Science, Pilani}{Aug 2016 -- July 2020}
      {Bachelor of Engineering (Electronics and Instrumentation)}{}
  \resumeSubHeadingListEnd


%-----------PUBLICATIONS-----------
\section{Publications}
\resumeSubHeadingListStart

    \resumeItem{\textbf{A. Sharma}, S. Gupta, S. Singh, R.D. Yadav, H. Song, W. Pan, S. Roy and S. Baldi, \href{https://drive.google.com/file/d/1HkqkOmhag8Z2A9fPm0qs8W_QRIauPzrB/view?usp=drive_link}{\textit{``Impedance and Stability Targeted Adaptation for Aerial Manipulator with Unknown Coupling Dynamics''}}, Proceedings of the 25th International Conference on Control, Automation, and Systems (ICCAS), 2025, in press.}
    
    \resumeItem{S. Gupta, \textbf{A. Sharma}, A. Mulgundkar, R.D. Yadav, and S. Roy, \href{https://ieeexplore.ieee.org/abstract/document/10711418}{\textit{``Adaptive Control of Quadrotor under Actuator Loss and Unknown State-dependent Dynamics''}}, at the 2024 IEEE 20th International Conference on Automation Science and Engineering, doi: 10.1109/CASE59546.2024.10711418}
    
    \resumeItem{R.D. Yadav, B. Jones, S. Gupta, \textbf{A. Sharma}, J. Sun, J. Zhao and S. Roy, \href{https://ieeexplore.ieee.org/abstract/document/11098573}{\textit{``An integrated approach to aerial grasping: Combining a bistable gripper with adaptive control''}}, in \textit{IEEE/ASME Transactions on Mechatronics}, doi: 10.1109/TMECH.2025.3586888}
    
\resumeSubHeadingListEnd

%-----------TECHNICAL REPORTS-----------
\section{Technical Reports and Under Review}
\resumeSubHeadingListStart
  \resumeItem{\textbf{A. Sharma}, S. Gupta, R.D. Yadav, W. Pan, S. Roy, and S. Baldi, \href{https://drive.google.com/file/d/1c9CXoG8qclpZkv1j3IWnG-tqjfvcdm9N/view?usp=drive_link}{\textit{``Achieving Adaptive Impedance Control for Autonomous Aerial Manipulation under Unknown Dynamics''}}, under review at \textit{IEEE/ASME Transactions on Mechatronics}, 2025.}
  \resumeItem{S. Gupta, \textbf{A. Sharma}, R.D. Yadav, S. Roy, W. Pan, and S. Baldi, \href{https://drive.google.com/file/d/1-EzHzwyE7rtqakK8MWYf0iBJYJWjJdl7/view?usp=drive_link}{\textit{``A Switched Adaptive Control Framework for Aerial Manipulators Under Dynamic Transitions''}}, under review at \textit{IEEE Transactions on Robotics}, 2025.}
\resumeSubHeadingListEnd


%-----------Under Review-----------
\section{Ongoing Projects}
\resumeSubHeadingListStart

  \resumeSubheading
      {Reinforcement Learning Based Control for Robotic Arms in Aerial Manipulation}{}
      {Robotics Research Center, IIIT Hyderabad}{}
      \resumeItemListStart
        \resumeItem{Creating custom simulation environments in Nvidia IsaacLab for training RL agents for aerial manipulators with a 2-DOF robotic arm.}
        \resumeItem{Learning policies for efficient interaction behavior for the robotic arm via PPO using state and end-effector force feedback}
        % \resumeItem{Achieving improved manipulation accuracy and reduced energy consumption compared to classical controllers}
      \resumeItemListEnd
      
  \resumeSubheading
      {Diffusion Models for Robust System Identification}{}
      {Collaboration with University of Manchester}{}
      \resumeItemListStart
        \resumeItem{Researching novel applications of diffusion models for system identification in aerial manipulators}
        \resumeItem{Developing parameter estimation techniques that are robust to model uncertainties and environmental disturbances}
        \resumeItem{Implementing PyTorch-based framework for online learning of dynamic parameters during flight operations}
      \resumeItemListEnd
  
\resumeSubHeadingListEnd

%----------Experience----------

\section{Experience}
    \resumeSubHeadingListStart
    
        \resumeSubheading{\small Research Associate, \textnormal{\emph{Non-Linear Control for Aerial Manipulation}}}{\small Aug 2022 -- Present}{Supervisor: Dr. Spandan Roy}{Robotics Research Center, IIIT Hyderabad.}
            \resumeItemListStart
                \resumeItem{Working on non-linear control algorithms for aerial manipulators including adaptive control, switched controllers, and impedance controllers. Analyzing the role of impedance control methodologies to add compliance in aerial manipulation.}
            \resumeItemListEnd

        \vspace{-0.4cm}
            
        \resumeSubheading{\small Teaching Assistant, \textnormal{\emph{Robotics -- Dynamics and Control; Mechatronics System Design}}}{\small Monsoon 2023; Spring 2025}{Supervisors: Dr. Nagamanikandan Govindan, Dr. Spandan Roy and Dr. Harikumar Kandath}{IIIT Hyderabad.}
            \resumeItemListStart
                \resumeItem{Drafted and graded assignments, quizzes, projects, and exam papers; conducted weekly doubt-clearing sessions.}
            \resumeItemListEnd


        \resumeSubheading{\small Research Associate, \textnormal{\emph{Controller Design for Super-maneuvering Fighter Aircraft}}}{\small Jan 2020 -- June 2020}
        {Supervisor: Dr. Bijoy Krishna Mukherjee}{EEE, BITS Pilani.}
            \resumeItemListStart
                \resumeItem{Worked on designing a H-infinity optimal controller for F-18 High Alpha Research Vehicle (HARV) and tested it for Herbst maneuver in Matlab and Simulink.}
            \resumeItemListEnd


        \resumeSubheading{\small Project Associate, \textnormal{\emph{Design of an Intelligent Fuzzy Controller for Flow control systems}}}{\small Aug 2019 -- Dec 2019}
        {Supervisor: Dr. Puneet Mishra}{EEE, BITS Pilani.}
            \resumeItemListStart
                \resumeItem{Used the Takagi-Sugeno model to design an Intelligent fuzzy controller for rectification of stiction based non-linearities in pneumatic valves and tested it on a flow control plant setup. Compared the designed controller against the PID controller using the IAE and ITAE performance indices.}
            \resumeItemListEnd
        
    \resumeSubHeadingListEnd


%-----------Research collabration-----------
\section{Research Collaborations}
 \begin{itemize}[leftmargin=0.15in, label={}]
  \vspace{2pt} 
    \small{\item{
     \textbf{Simone Baldi}: Southeast University, Nanjing, China and guest with Delft Center for Systems and Control, TU Delft.\\
     \textbf{Wei Pan}: University of Manchester, England.\\
     \textbf{Jianguo Zhao}: Head Adaptive Robotics Lab, Colorado State University, USA.\\
    %  \textbf{Arun Kumar Singh} University of Tartu, Estonia.
    }}
 \end{itemize}
 \vspace{-16pt}



%----------TECHNICAL SKILLS----------
\section{Technical Skills}
\resumeItemListStart
  \resumeItem{\textbf{Languages:} Python, C/C++, MATLAB, Bash}
  \resumeItem{\textbf{AI \& Control Libraries:} PyTorch, TensorFlow, SKRL - Reinforcement Learning library, Stable-Baselines3, SciPy, Control Toolbox}
  \resumeItem{\textbf{Middleware \& Planning:} ROS 1, ROS 2, MoveIt 2, micro-ROS}
  \resumeItem{\textbf{Simulation \& Flight:} Gazebo, IsaacSim, IsaacLab, PX4 SITL/HITL, MAVROS}
  \resumeItem{\textbf{DevOps \& Tooling:} Docker, Docker Compose, Git/GitHub, VS Code Dev Containers}
  \resumeItem{\textbf{Hardware \& Sensors:} Pixhawk 2.4.8, CUAV X7, NVIDIA Jetson, Dynamixel XM430, OptiTrack MoCap, Robotous RFT60, LiDAR, RGB-D cameras}
\resumeItemListEnd

% %-----------ACADEMIC PROJECTS-----------
% \section{Relevant Academic Projects}
% \resumeSubHeadingListStart
      
%     \resumeSubheading
%       {Diffusion Models for Robust System Identification}{Aug 2023 -- Present}
%       {Collaboration with University of Manchester}{}
%       \resumeItemListStart
%         \resumeItem{Researching novel applications of diffusion models for system identification in aerial manipulators}
%         \resumeItem{Developing parameter estimation techniques that are robust to model uncertainties and environmental disturbances}
%         \resumeItem{Implementing PyTorch-based framework for online learning of dynamic parameters during flight operations}
%       \resumeItemListEnd
      
%       \resumeItemListEnd
      
% \resumeSubHeadingListEnd

%-----------COURSES------------------------

%-----------RELEVANT COURSES---------------
%-----------RELEVANT COURSES---------------
\section{Relevant Courses}
\resumeItemListStart
  \resumeItem{\textbf{Graduate:} Robotics: Dynamics and Control; Mobile Robotics; Advances in Robotics and Control; Topics in Applied Optimization; Mechatronic System Design}
  \resumeItem{\textbf{Undergraduate:} Robotics; Internet of Things (IoT); Control Systems; Control Systems Lab; Industrial Instrumentation and Control; Medical Instrumentation}
  \resumeItem{\textbf{Audited Courses:} Statistical Methods in Artificial Intelligence; Computer Vision}
\resumeItemListEnd
%-----------INVOLVEMENT---------------
\section{Key Highlights}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Scholarships}  \emph{}}{}
          \resumeItemListStart
            \resumeItem {IIIT Hyderabad research student fellowship to cover tuition fee during Masters program. (Aug 2022 - Present) }
          \resumeItemListEnd
           \vspace{4pt}  

           {\textbf{\small Responsibilities and Volunteering } \emph{}}{}
           \vspace{-2pt} 
          \resumeItemListStart
  \resumeItem{Member of Student Parliament, IIIT-H (2024-2025))}
  \resumeItem{Student Volunteer, Student Union - BITS Pilani (2016-2017) }
\resumeItemListEnd
           \vspace{4pt}  
          
          {\textbf{\small Achivements } \emph{}}{}
           \vspace{-2pt} 
          \resumeItemListStart
  \resumeItem{Ranked \textbf{582nd} in Graduate Aptitude Test in Engineering (Feb 2021)}
  \resumeItem{Scored within the \textbf{99th} percentile nationwide in BITSAT (May 2016)}
  \resumeItem{Ranked \textbf{125th} in the State Engineering Test (CGPET, Apr 2016)}
\resumeItemListEnd
           \vspace{-8pt}  
          
        \resumeProjectHeading
          {\textbf{Presentations}\emph{}}{}
          \resumeItemListStart
            \resumeItem{Paper Oral Presentation in CASE 2024.}
            \resumeItem{Poster Presentation of autonomous aerial manipulation project during IIIT-H R\&D Showcase 2024 and 2025.}
          \resumeItemListEnd
          \vspace{2pt}  
          
    \resumeSubHeadingListEnd


    %----------REFERENCES----------
\section{Referrals}
\resumeSubHeadingListStart

  \resumeSubheading
      {Dr. Spandan Roy}{Assistant Professor, Robotics Research Center, IIIT-H}{spandan.roy@iiit.ac.in}{+91 8777735183}

  \resumeSubheading
      {Dr. Puneet Mishra}{Assistant Professor, EEE, BITS Pilani}{puneet.mishra@pilani.bits-pilani.ac.in}{+91 8010443127}

  % \resumeSubheading
  %     {Dr. Wei Pan}{Senior Lecturer (Associate Professor), The University of Manchester}{wei.pan@manchester.ac.uk}{}

\resumeSubHeadingListEnd

\end{document}

